%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------
\begin{acknowledgements}
This master's journey changed my life, my knowledge improved, I feel mature and stronger.
\bigbreak
Although I am the one writing this thesis to finalise but the journey to the finish line would have never been possible without the blessings, wishes and hopes of the people whom I mentioned here.
\bigbreak
First acknowledgment to my Father Arvind Kumar Singh, my Mother Saraswati Singh, my brother in law Nidish and to my wife Pooja who suggested to take this course.
\bigbreak
Second, to my line managers Sameer Sheety and Hans Vancompernolle who supported me with the decision. I am very thankful for their continuous support during the course program.
\bigbreak
Then to the participants of the Focus Group for the validation session.
1) Barry Derksen
2) Joshua Paffen
3) Marcel de Haan
4) Mark Butterhoff
5) Nico Kuijper
6) Rion Rijker 
7) Pascale van Damme

\bigbreak
At the Antwerp Management School side, my sincere thanks to Stevan de Haes and Danny Lauwerns for considering my application and allowing to pursue this course. Their help and flexibility is beyond the scope of my write up.
\bigbreak
And now to my friends at AMS, I made a good reputation and connection with almost every one, but I must mention the special one here because of their support to me in one or another way. Theo, Jan, Dave, Titi, Gafoor, Tapan, Jousua, Amie, Nick, Laurence, Stefan, Jeroen, Benoit, Tim, Dorian, Chao, Maria, Joris, Pascale, Ahemad and the list is never ending. I am really lucky to have a very nice group of people in 2018-2020 batch. Edzo is the one who supported me at almost every part of my research and finalising this thesis.
\bigbreak
I am also grateful to ON2IT Research and Development department(Jean-Hugues Migeon and Jeroen Scheerder) for helping me understand the domain quickly,  my three proof readers Edzo Botjes, Hatem Smine and Tapan Kumar who helped reviewing this work.
\bigbreak
Finally, a very special thanks to Yuri Bobbert Sir for his belief in my potential. Thanks to his direction, his time and effort investments in me, it was a real boom, and I know he is the real "Guru", my project advisor\ldots


\end{acknowledgements}

%----------------------------------------------------------------------------------------